Position Paper: Against Spurious Understanding- Dovelating Inflated AI Claims \raisebox{-6pt}{\includegraphics[scale=0.09]{dove_1f54a-fe0f.png}}

### 2024-02-01 main.tex
uh
Updates from Overleaf

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Against Spurious Understanding: Dovelating Inflated AI Claims}

@@

\twocolumn[
\icmltitle{Against Spurious Understanding: 
           Dovelating Inflated AI Claims \raisebox{-6pt}{\includegraphics[scale=0.09]{dove_1f54a-fe0f.png}}}

@@

Noticing these trends, we as the authors of this article are concerned. We feel that the current culture of racing towards Big Outcome Statements in industry and academic publishing too much disincentivizes efforts towards more thorough and nuanced actual problem understanding. At the same time, as the outside world is so eager to adopt AI technology, (too) strong claims make for good sales pitches, but a question is whether there indeed sufficient evidence for these claims. With successful A(G)I outcomes needing to look human-like, this also directly plays into risks of anthropomorphizing (the attribution of human-like qualities to non-human objects) and confirmation bias (the seeking-out and/or biased interpretation of evidence in support of one's beliefs). In other words, it is both very tempting to claim surprising human-like achievements of AI, and as humans we are very prone to genuinely believe this.

@@

In Winter 2023, a research article went viral on the X\footnote{\url{https://twitter.com/wesg52/status/1709551516577902782?s=20}} (formerly Twitter) platform~\cite{gurnee2023languagev1}. In this paper, through linear probing experiments, the claim was made that LLMs learned literal maps of the world, and as such were more than `stochastic parrots'~\cite{bender2021dangers} that can only correlate and mimic existing patterns from data, but not understand truly understand it.

@@

In this, as the quest for AGI so deeply roots in human-like recognition, we also want to put an explicit word of warning about use of terminology. Many terms used in current A(G)I research (e.g.\ emergence, intelligence, learning, `better than human' performance) have common understanding in specialized research communities, but have bigger, anthropormophic connotations in laypersons.

>>>>

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Position Paper: Against Spurious Understanding: Dovelating Inflated AI Claims}

@@

\twocolumn[
\icmltitle{Position Paper: Against Spurious Understanding- 
           Dovelating Inflated AI Claims \raisebox{-6pt}{\includegraphics[scale=0.09]{dove_1f54a-fe0f.png}}}

@@

Noticing these trends, we as the authors of this article are concerned. We feel that the current culture of racing towards Big Outcome Statements in industry and academic publishing too much disincentivizes efforts towards more thorough and nuanced actual problem understanding. At the same time, as the outside world is so eager to adopt AI technology, (too) strong claims make for good sales pitches, but a question is whether there is indeed sufficient evidence for these claims. With successful A(G)I outcomes needing to look human-like, this also directly plays into risks of anthropomorphizing (the attribution of human-like qualities to non-human objects) and confirmation bias (the seeking-out and/or biased interpretation of evidence in support of one's beliefs). In other words, it is both very tempting to claim surprising human-like achievements of AI, and as humans we are very prone to genuinely believe this.

@@

In Winter 2023, a research article went viral on the X\footnote{\url{https://twitter.com/wesg52/status/1709551516577902782?s=20}} (formerly Twitter) platform~\cite{gurnee2023languagev1}. In this paper, through linear probing experiments, the claim was made that LLMs learned literal maps of the world, and as such were more than `stochastic parrots'~\cite{bender2021dangers} that can only correlate and mimic existing patterns from data, but not truly understand it.

@@

In this, as the quest for AGI so deeply roots in human-like recognition, we also want to put an explicit word of warning about use of terminology. Many terms used in current A(G)I research (e.g.\ emergence, intelligence, learning, `better than human' performance) have common understanding in specialized research communities, but have bigger, anthropormophic connotations in laypersons. We add our voice to emerging calls for this~\cite{shanahan2024talking}.
